Cooperación y ergodicidad

### 2021-09-14 notas.tex
Code: the cooperative time average by size of the group, environment and strategy

\begin{quotation}
    The central idea I am developing here is that an essential part of evolution deals with adaptation to changing environmental conditions~\cite{pigliucci2001-plasticity}.
\end{quotation}

@@

Ya Den Boer plantea como hipótesis un trade-off del ``spreading of the risk'', respecto de la densidad poblacional.
Seger se pregunta
\begin{quotation}
    Is there am evolutionary trade-off between \emph{expected} fitness and the \emph{variance} of fitness?
    Here, we show why there is only under certain circumstances~\cite{seger1987-betHedging}.

@@

    To be able to survive and reproduce, individuals often need to exhibit adaptations that respond to the diversity of conditions of life that they may encounter.
    Bet-hedging in evolutionary biology is usually defined as a strategy or allele that increases the probability of its fixation by lowering the variance of fitness.
    A strict definition of bet-hedging states that the bet-hedger should have paid a cost of a reduced mean.

>>>>

\begin{quotation} \cite{gillespie1974-variance}
    The variance in the numbers of offspring of a genotype has two components, the within-generation component resulting from different individuals of the same genotype having different numbers of offspring, and a between-generation component due to the effects of a changing environment.
    This latter component has been recently investigated (GILLESPIE 1973); the former will be explored in this paper.
\end{quotation}

@@

Ya Den Boer plantea como hipótesis un trade-off del ``spreading of the risk'', respecto de la densidad poblacional.
Seger se pregunta
\begin{quotation} \cite{denBoer1968-spreadingRisk}:
    Is there am evolutionary trade-off between \emph{expected} fitness and the \emph{variance} of fitness?
    Here, we show why there is only under certain circumstances~\cite{seger1987-betHedging}.

@@
